---
title: "SDS 237 - Field Journal"
author: "Anny(Jiaqi) Li"
date: "Last updated on `r Sys.Date()`"
output: pdf_document
---

> Instructions: For each journal entry, first fill out the metadata for that entry by entering your name, the date you observed a data environment, the date you wrote up your entry, and the location of the environment you observed in between the quotation marks of the associated code snippet. Be sure to enter the date as month/day/year. Below this code snippet, write your journal entry. Once your done, knit the document and push your changes to GitHub.

```{r libraries, include = FALSE}
library(lubridate)
```

## Journal Entry 1

```{r metadata_1, echo=FALSE, results='asis'}
observer_1 <- "Anny(Jiaqi) Li"
date_observed_1 <- mdy("0/29/2022")
date_written_up_1 <- mdy("03/01/2022")
location_1 <- "Chase House 1st floor"

cat(paste0("This entry documents a data environment ", observer_1, " observed on ", date_observed_1, " in ", location_1, ". The observations were written up on ", date_written_up_1, "."))
```

My friend M and me were having a conversation about the limitations of Big Data. 

While doing her CS homework in the living room of Chase House, M started talking about how strongly she believed in the predictive and calculating power of Big Data. “I believe that everything in this material world interact with each other and all the phenomenon, whether observed or not by humans, is a result of such interaction” M said with an excitement on her face. She continued: “Since Big Data is capable of discovering the pattern and interaction hiding behind different data, if we could gather enough data that captures everything in the physical world, then we can even predict the future. ” Her argument reminded me of the classical determinist idea ---- Laplace’s demon, which states that if we know how every atom in the universe work, then we could plug this information into a formula and predict the future. It is indeed very exciting to imagine the scenario where humans have full control of everything in the world. 

However, technology we have today is not advanced enough to measure and collect everything and I highly doubt that we would ever be able to do that. The Uncertainty Principle in Quantum Physics has already proposed the idea that the position and velocity of atoms cannot be both measured exactly in theory, and the closest measurement we could reach is probability cloud, which only provides us a probability of detecting a given particle in a certain space. Though this principle is not necessarily true, it still makes me to think that there are limitations to the capability of Big Data. Besides the limitation of its capability, Big Data employs mostly **inductive reasoning** because it collects data based on observations, come up with a model to best explain the relationship between data, which could be called generalization, and finally arrive at its conclusion. Unlike **deductive reasoning**, starting from a paradigm, inductive reasoning could not guarantee the conclusion is 100% true even with extremely strong evidence supporting it.  
An **interpretivist** could argue that no matter how strong the association between two variables are, it could be just an illusion.

After hearing my view about Big Data, M refuted: “If everyone is as nihilistic as you, the society would achieve nothing, it would be a total failure”.  The discussion of **epistemology** of big data, which concerns about what makes data and what counts as valuable data and so on, must continue because it determines the direction of research in a fundamental way.


## Journal Entry 2 

```{r metadata_2, echo=FALSE, results='asis'}
observer_2 <- "Jiaqi Li"
date_observed_2 <- mdy("03/16/2022")
date_written_up_2 <- mdy("03/22/2022")
location_2 <- "Hotel lounge"

cat(paste0("This entry documents a data environment ", observer_2, " observed on ", date_observed_2, " in ", location_2, ". The observations were written up on ", date_written_up_2, "."))
```

Recently I am applying for summer internships, and one thing strikes me, as an international student, is how U.S companies specifically ask candidates’ to identify themselves with one of the race classifications: White, Black, Latino, American Indian/Alaska Native, Asian, or Pacific Islander. I’ve worked for companies based in both Europe and Asia before, but none of the companies that I know ask about races. Rather, they usually ask about the country of citizenship, or the country that the person grew up in. That’s when I realized that race is actually a very American thing, a human-constructed thing. The identity of White, Black or Asian are somewhat made and reinforced by a set of discriminatory policies such as the Jim Crow law and the Chinese Exclusion Act.

My Asian friend X's experience probably could best illustrate this. 

X was a bit drunk that day because it was our first day in Cancun. She got really excited and drank more than usual. We were joking that even Cancun is full of white frat boys. Then she started open up more.

X was born and raised in New Jersey, which didn’t have a large Asian population, compared to the West Coast. She told me that she was very used to being the Asian token friend in the friend circle. On the bright side, she got to introduce her White friends to Asian culture, taking them to Korean BBQ, and watching anime together. But she never is an anime fan, though it is good to watch a few episodes sometimes to kill time, and prefers spicy food because her Chinese mom from Sichuan loves it. She was just introducing her White friends to a small part of Asian culture that is considered acceptable here in the United States, playing the role of the typical Asian friend who is into anime and K-pop, because she knew from a very young age that exhibiting unacceptable Asian traits can bring consequences.

Fitting into the average Asian image was not the only task, X also wanted to break the Asian stereotype, showing that she was not like other Asians. She wanted to be “that cool Asian kid”. X tried joining the cross country club in middle school, to be more athletic, but she had tutor session to go to after school so she quit eventually. The conflict between trying to be the average Asian and wanting to be seen differently than other Asians lasted throughout her teenage years. The label “Asian” clearly has much influence on her, and the **looping effect** is obvious.


## Journal Entry 3

```{r metadata_3, echo=FALSE, results='asis'}
observer_3 <- "FILL YOUR NAME"
date_observed_3 <- mdy("01/01/1990")
date_written_up_3 <- mdy("01/01/1990")
location_3 <- "FILL LOCATION"

cat(paste0("This entry documents a data environment ", observer_3, " observed on ", date_observed_3, " in ", location_3, ". The observations were written up on ", date_written_up_3, "."))
```

[Enter your write-up here.]

## Journal Entry 4

```{r metadata_4, echo=FALSE, results='asis'}
observer_4 <- "FILL YOUR NAME"
date_observed_4 <- mdy("01/01/1990")
date_written_up_4 <- mdy("01/01/1990")
location_4 <- "FILL LOCATION"

cat(paste0("This entry documents a data environment ", observer_4, " observed on ", date_observed_4, " in ", location_4, ". The observations were written up on ", date_written_up_4, "."))
```

[Enter your write-up here.]

## Journal Entry 5

```{r metadata_5, echo=FALSE, results='asis'}
observer_5 <- "FILL YOUR NAME"
date_observed_5 <- mdy("01/01/1990")
date_written_up_5 <- mdy("01/01/1990")
location_5 <- "FILL LOCATION"

cat(paste0("This entry documents a data environment ", observer_5, " observed on ", date_observed_5, " in ", location_5, ". The observations were written up on ", date_written_up_5, "."))
```

[Enter your write-up here.]

